Analysis of Physical Activity Survey(2022)

### 2022-04-27 outputs/paper/paper.Rmd
Almost finished.

## Weaknesses and next steps

@@

	- The sample was from the 50 states of the United States and the District of Columbia as well as Peurto Rico and the sampling strategy of cross-sectional household interview survey.

@@

	- NHIS surveys are approved and review by the ICF Institutional Review Board( IRB).[@citeDHS_Ethics].

>>>>

  According to [@citeMuscle] "meeting both aerobic and muscle-strengthening exercise guidelines was associated with a lower obesity prevalence, and associations were more pronounced for higher obesity classes." We found similar section \@ref(Results). However we also noted in the model that muscle training and aerobic activities did not fully explain the obesity problems of the United States. Suggesting that while physical activity may be important it is not the entire explanation for the increasing rates of obesity.[@citeNutrition]
## Weaknesses and next steps

  Although this analysis found some links between aerobic activity and muscle training to rates of obesity in the United States. It is clear that there is more to the story of obesity in the United States then just the level of physical activity. Next steps for analysis would be researching diet along with excercise. Data in this area in the last 2 years during the pandemic would also be particularly interesting. Particularly in comparing states which had more restricted access to public fitness facilities like gyms and public parks compared to those states which did not employ as strict restrictions, re-opened earlier, or states like Montana which had less population density and more opportunity to open air fitness training compared to densely populated states such as New York.

@@

	- The sample was from the 50 states of the United States and the District of Columbia and the sampling strategy of cross-sectional household interview survey.

@@

	- NHIS surveys are approved and review by the ICF Institutional Review Board( IRB).[@citeNHIS_Ethics].
